\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours

### 2021-08-31 manuscript.Rmd
Updates

```
Sampling adequacy was investigated by Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy . The overall KMO vale for 23 items was `r printnum(KMO$MSA)` which was above the cutoff value of .50 indicating a mediocre sample [@RN1179].
# Confirmatory Factor Analysis
# Confirmatory Factor Analysis

>>>>

```
Sampling adequacy was investigated by Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy[@kaiserIndexFactorialSimplicity1974] . The overall KMO vale for 23 items was `r printnum(KMO$MSA)` which was above the cutoff value of .50 indicating a mediocre sample [@hutchesonMultivariateSocialScientist1999].
# Confirmatory Factor Analysis
# Confirmatory Factor Analysis
